---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = F,
  message = F
)
```

# aquaras

<!-- badges: start -->
  [![R-CMD-check](https://github.com/Klorator/aquaras/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Klorator/aquaras/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of aquaras is to make it easier to create runlists for use with MassLynx (Waters LC/MS software) and also facilitate some of the data processing steps with the MassLynx complete summary output file.

## Installation

You can install the development version of aquaras from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Klorator/aquaras")
```

## Example workflow:

### Summary
* Call `RunlistGenerator()`
* Input all the runlist info under "Well input"
  * Optionally: download/upload the tsv under "Full list" to save/resume a project
* Generate a runlist under "Runlist" and download the tsv
* Do the experiments. Yeay!
* Call `SplitOutput.ML()` and select the MassLynx complete summary output file (the file-selection window might be hiding behind RStudio)
* Analyze the results for each compound
* Publish paper!
* Design new experiments (rinse and repeat)

### Pre-LC/MS
Here is a mock example of a populated runlist.
```{r example runlist}
library(aquaras)
# str(Example_Runlist)
Example_Runlist[c(1:2, 7:8, 13:14), c(1, 5, 8, 12, 14)]
```

And this is what we get from generating a final runlist version with default settings.
```{r generated runlist}
Final_Runlist = create.Runlist(Example_Runlist)
Final_Runlist[c(1, 5, 8, 12, 14)]
```

Ready for pasting columns into MassLynx!

### Post-LC/MS examples
Recommended to place your output file in it's own folder.
Run `SplitOutput.ML()` and select the output file.

## Planned features

### Plotting of graphs

```{r plotting}
# Plotting with ggplot2 here...
```

