---
title: "Introduction to aquaras"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to aquaras}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = F,
  message = F
)
```

```{r setup}
library(aquaras)
```
## Overview

##### Pre-LC/MS run
Provides tools for working with runlists to use with MassLynx (Waters LC/MS software).  Calling `ras.RunlistGenerator()` launches a Shiny app that lets you create the full data frame and a runlist. Alternatively, `ras.create.Runlist()` may be used directly.

##### Post-LC/MS run
Use `ras.SplitOutput()` to split the MassLynx complete summary output file into individual data frames and write them to files. Unless `clean = FALSE`, this removes blanks and splits the `Name` and `Sample Name` columns according to the pre-LC/MS template. To only return the list of data frames and not write to the file system, use `write = FALSE`.

##### Workflow summary
* Call `ras.RunlistGenerator()`
* Input all the runlist info under "Well input"
  * Optionally: download/upload the tsv under "Full list" to save/resume a project
* Generate a runlist under "Runlist" and download the tsv
* Do experiments. Yeay!
* Call `ras.SplitOutput()` and select the MassLynx complete summary output file (the file-selection window might be hiding behind RStudio)
* Analyze the results for each compound
* Publish paper!
* Design new experiments (rinse and repeat)

## Example workflow
#### Pre-LC/MS
Here is a mock example of a populated runlist.
```{r example runlist}
# str(Example_Runlist) # Run this in the console yourself
# View(Example_Runlist) # Run this in the console yourself
ras.Example_Runlist[c(1:2, 7:8, 13:14), c(1, 5, 8, 12, 14)]
```

And this is what we get from generating a final runlist version with default settings.
```{r generated runlist}
Final_Runlist = ras.create.Runlist(ras.Example_Runlist)
Final_Runlist[c(1, 5, 8, 12, 14, 16)]
```

Ready for pasting columns into MassLynx!

#### Post-LC/MS
Recommended to place your output file in it's own folder.

Run `ras.SplitOutput()` and select the output file.

This splits the output into its constituent data frames and (unless `write = FALSE`) writes them as individual .txt files in the same directory as the source file. Naming convention used is "[source file name] - [compound name]". `clean = FALSE` may be used to not perform any data manipulation at this stage. This is recommended if the source file was not created using the {aquaras} standard format.
