---
title: "Introduction to aquaras"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to aquaras}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aquaras)
```
Created primarily for personal use, all the better if anyone else finds this helpful.  

### Pre-LC/MS run:
Provides tools for working with runlists to use with MassLynx (Waters LC/MS software).  Calling RunlistGenerator() launches a Shiny app that lets you create the full data frame and a runlist. Alternatively, create.Runlist() may be used directly.

### Post-LC/MS run: 
Use SplitOutput.ML() to split the MassLynx complete summary output file into individual data frames and write them to files. Unless clean = FALSE, this removes blanks and splits the "Name" and "Sample Name" columns according to the pre-LC/MS template.

### Example workflow:
* Call `RunlistGenerator()`
* Input all the runlist info under "Well input"
  * Optionally: download/upload the tsv under "Full list" to save/resume a project
* Generate a runlist under "Runlist" and download the tsv
* Do the experiments. Yeay!
* Call `SplitOutput.ML()` and select the MassLynx complete summary output file (the file-selection window might be hiding behind RStudio)
* Analyze the results for each compound
* Publish paper!
* Design new experiments (rinse and repeat)

```{r}

```

